KidsAIR: Main analysis secondary models

### 2020-11-02 main_analysis_secondary_models.Rmd
data cleaning/analysis updates

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  #scale_shape_manual(values = c(15, 16, 17, 18, 13, 9)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "Systolic BP ITT models") +
  labs(y = "LRTI events per child-week at risk \n compared to placebo treatment") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates
```

@@

@@

# Run results through function, save, combine for plotting
itt_pm_tidy <- results_function(itt_pm_results, "ITT Primary")
itt_pm_income_tidy <- results_function(itt_pm_income_results, "ITT + income")
itt_pm_education_tidy <- results_function(itt_pm_education_results, "ITT + education")
itt_pm_smoke_tidy <- results_function(itt_pm_smoke_results, "ITT + smoke hx")
itt_pm_burn_level_tidy <- results_function(itt_pm_burn_level_results, "ITT + burn level")
itt_pm_home_tidy <- results_function(itt_pm_home_results, "ITT home only")
itt_pm_no_age_tidy <- results_function(itt_pm_no_age_results, "ITT - age")
itt_pm_outlier_tidy <- results_function(itt_pm_outlier_results, "ITT outlier")

itt_pm_results_combined <- rbind(itt_pm_tidy, itt_pm_income_tidy, itt_pm_education_tidy, 
                              itt_pm_smoke_tidy, itt_pm_burn_level_tidy, itt_pm_home_tidy,
                              itt_pm_no_age_tidy, itt_pm_outlier_tidy)

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT home only",
                                   "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  #scale_shape_manual(values = c(15, 16, 17, 18, 13, 9)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "Systolic BP ITT models") +
  labs(y = "Difference in PM2.5 \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = .8, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates
```

>>>>

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "LRTI events per child-week at risk \n compared to placebo treatment") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

ggsave("itt_plot_estimates.jpg", width = 12, height = 6)
```

@@

itt_pm_smoking_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | home:cohort:area) + 
                                   home_act_smoking_sum, data = analysis_data)

itt_pm_windows_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | home:cohort:area) + 
                                   home_act_windows_sum, data = analysis_data)

itt_pm_door_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | home:cohort:area) + 
                                   home_act_door_sum, data = analysis_data)

itt_pm_sweep_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | home:cohort:area) + 
                                   home_act_sweep_sum, data = analysis_data)

@@

# Run results through function, save, combine for plotting
itt_pm_tidy <- results_function(itt_pm_results, "ITT Primary")
itt_pm_income_tidy <- results_function(itt_pm_income_results, "ITT + income")
itt_pm_education_tidy <- results_function(itt_pm_education_results, "ITT + education")
itt_pm_smoke_tidy <- results_function(itt_pm_smoke_results, "ITT + smoke hx")
itt_pm_burn_level_tidy <- results_function(itt_pm_burn_level_results, "ITT + burn level")
itt_pm_smoking_tidy <- results_function(itt_pm_smoking_results, "ITT + smoke act")
itt_pm_windows_tidy <- results_function(itt_pm_windows_results, "ITT + window act")
itt_pm_door_tidy <- results_function(itt_pm_door_results, "ITT + door act")
itt_pm_sweep_tidy <- results_function(itt_pm_sweep_results, "ITT + sweep act")
itt_pm_home_tidy <- results_function(itt_pm_home_results, "ITT home only")
itt_pm_no_age_tidy <- results_function(itt_pm_no_age_results, "ITT - age")
itt_pm_outlier_tidy <- results_function(itt_pm_outlier_results, "ITT outlier")

itt_pm_results_combined <- rbind(itt_pm_tidy, itt_pm_income_tidy, itt_pm_education_tidy, 
                              itt_pm_smoke_tidy, itt_pm_burn_level_tidy, itt_pm_smoking_tidy,
                              itt_pm_windows_tidy, itt_pm_door_tidy, itt_pm_sweep_tidy,
                              itt_pm_home_tidy, itt_pm_no_age_tidy, itt_pm_outlier_tidy)

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "Difference in PM2.5 \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

ggsave("itt_pm_plot_estimates.jpg", width = 12, height = 6)
```

Sensitivity analyses for ER framework, LRTI outcome

```{r}
# Run model variations
er_results <- glmer.nb(lrti_events ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + 
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)

er_income_results <- glmer.nb(lrti_events ~ pm_mean_sampling_period_iqr + child_age + 
                          income_3level + residents_smoke + 
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)

er_burn_level_results <- glmer.nb(lrti_events ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + burn_level_3level +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)

er_smoking_results <- glmer.nb(lrti_events ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + home_act_smoking_sum + 
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)

er_windows_results <- glmer.nb(lrti_events ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + home_act_windows_sum +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)

er_door_results <- glmer.nb(lrti_events ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + home_act_door_sum +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)

er_sweep_results <- glmer.nb(lrti_events ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + home_act_sweep_sum +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)

er_home_results <- glmer.nb(lrti_events ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + home_act_windows_sum +
                          (1 | home) + offset(log_person_time_at_risk), 
                          data = analysis_data)

er_no_age_results <- glmer.nb(lrti_events ~ pm_mean_sampling_period_iqr + 
                          education_3level + residents_smoke + 
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)

er_outlier_results <- glmer.nb(lrti_events ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + 
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data_outliers)

tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("pm", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = "PM2.5",
         model = model_name) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results

# Run results through function, save, combine for plotting
er_tidy <- results_function(er_results, "ER Primary")
er_income_tidy <- results_function(er_income_results, "ER + income")
er_burn_level_tidy <- results_function(er_burn_level_results, "ER + burn level")
er_smoking_tidy <- results_function(er_smoking_results, "ER + smoke act")
er_windows_tidy <- results_function(er_windows_results, "ER + window act")
er_door_tidy <- results_function(er_door_results, "ER + door act")
er_sweep_tidy <- results_function(er_sweep_results, "ER + sweep act")
er_home_tidy <- results_function(er_home_results, "ER home only")
er_no_age_tidy <- results_function(er_no_age_results, "ER - age")
er_outlier_tidy <- results_function(er_outlier_results, "ER outlier")

er_results_combined <- rbind(er_tidy, er_income_tidy, er_burn_level_tidy, 
                              er_smoking_tidy, er_windows_tidy, er_door_tidy,
                              er_sweep_tidy, er_home_tidy, er_no_age_tidy,
                              er_outlier_tidy)

# Plot results
er_plot_estimates <- er_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ER Primary", "ER + income", "ER + burn level",
                                   "ER + smoke act", "ER + window act", "ER + door act",
                                   "ER + sweep act", "ER home only", "ER - age",
                                   "ER outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "LRTI cases per IQR increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "none",
          legend.text = element_text(size = 14, colour = "black")) 
er_plot_estimates

ggsave("er_plot_estimates.jpg", width = 12, height = 6)
```

Sensitivity analyses for LogReg framework, LRTI outcome

```{r}
# Run model variations
logreg_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + 
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

logreg_income_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + income_3level +
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

logreg_education_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + education_3level +
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

logreg_smoke_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + residents_smoke +
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

logreg_burn_level_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + burn_level_3level +
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

logreg_smoking_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + home_act_smoking_sum +
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

logreg_windows_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + home_act_windows_sum +
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

logreg_door_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + home_act_door_sum +
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

logreg_sweep_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + home_act_sweep_sum +
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

logreg_home_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + 
                       (1 | home), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

logreg_no_age_results <- glmer(lrti_events_di ~ treatment_assigned +  
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

logreg_outlier_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + 
                       (1 | home:cohort:area), data = analysis_data_outliers, 
                       family = binomial, offset = log_person_time_at_risk)

# Run results through function, save, combine for plotting
logreg_tidy <- results_function(logreg_results, "LR Primary")
logreg_income_tidy <- results_function(logreg_income_results, "LR + income")
logreg_education_tidy <- results_function(logreg_education_results, "LR + education")
logreg_smoke_tidy <- results_function(logreg_smoke_results, "LR + smoke hx")
logreg_burn_level_tidy <- results_function(logreg_burn_level_results, "LR + burn level")
logreg_smoking_tidy <- results_function(logreg_smoking_results, "LR + smoke act")
logreg_windows_tidy <- results_function(logreg_windows_results, "LR + window act")
logreg_door_tidy <- results_function(logreg_door_results, "LR + door act")
logreg_sweep_tidy <- results_function(logreg_sweep_results, "LR + sweep act")
logreg_home_tidy <- results_function(logreg_home_results, "LR home only")
logreg_no_age_tidy <- results_function(logreg_no_age_results, "LR - age")
logreg_outlier_tidy <- results_function(logreg_outlier_results, "LR outlier")

logreg_results_combined <- rbind(logreg_tidy, logreg_income_tidy, logreg_education_tidy, 
                              logreg_smoke_tidy, logreg_burn_level_tidy, logreg_smoking_tidy,
                              logreg_windows_tidy, logreg_door_tidy, logreg_sweep_tidy,
                              logreg_home_tidy, logreg_no_age_tidy, logreg_outlier_tidy)

# Plot results
logreg_plot_estimates <- logreg_results_combined %>%
  mutate(model = factor(model,
                        levels = c("LR Primary", "LR + income", "LR + education",
                                   "LR + smoke hx", "LR + burn level", "LR + smoke act",
                                   "LR + window act", "LR + door act", "LR + sweep act",
                                   "LR home only", "LR - age", "LR outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "Risk of LRTI event compared to Placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
logreg_plot_estimates

ggsave("logreg_plot_estimates.jpg", width = 12, height = 6)
```
